\begin{thebibliography}{9}
    \bibitem{ably23} Ably, \textit{Socket.IO vs. WebSocket\: Key differences and which to use}, [Online, URL\: \url{https://ably.com/topic/socketio-vs-websocket}, truy cập ngày 12\-01\-2023].
    \bibitem{akanbi15} Akanbi, O. A., Amiri, I. S., \& Fazeldehkordi, E. (2015), \textit{Feature Extraction. A Machine-Learning Approach to Phishing Detection and Defense}.
    \bibitem{cao16} Cao, X. H., Stojkovic, I., \& Obradovic, Z. (2016), \textit{A robust data scaling algorithm to improve classification accuracies in biomedical data}, BMC Bioinformatics.
    \bibitem{dumas18} Marlon Dumas, Marcello La Rosa, Jan Mendling, Hajo A. Reijers, (2018), \textit{Fundamentals of Business Process Management}, Springer.
    \bibitem{facebook23} Facebook Inc., Reactjs [Online, URL\: \url{https://react.dev/}, truy cập vào ngày 15\-12\-2023].
    \bibitem{jon10} Jon A. Krosnick and Stanley Presser (2010), \textit{Question and Questionnaire Design}, Handbook of Survey Research, Second Edition.
    \bibitem{kim19} Kim, S., Lee, J., \& Gweon, G. (2019), \textit{Comparing Data from Chatbot and Web Surveys}.
    \bibitem{krol14} Krol, M. W., de Boer, D., Delnoij, D. M., \& Rademakers, J. J. D. J. M. (2014), \textit{The Net Promoter Score \- an asset to patient experience surveys?}, Health Expectations.
    \bibitem{microsoft} Microsoft, \textit{N-tier architecture style}, [Online, URL\: \url{https://learn.microsoft.com/en-us/azure/architecture/guide/architecture-styles/n-tier}].
    \bibitem{mihelis01} Mihelis, G., Grigoroudis, E., Siskos, Y., Politis, Y., \& Malandrakis, Y. (2001), \textit{Customer satisfaction measurement in the private bank sector}, European Journal of Operational Research, 130(2).
    \bibitem{moira13} Moira Clark, Andrew Bryan (2013), \textit{Customer Effort: Help or hype?}, Henley Business School.
    \bibitem{prereport} Nguyễn Cảnh Hoàng, Nguyễn Ngọc Hiển, Nguyễn Việt Anh (2023), \textit{Ứng dụng hỗ trợ đánh giá quy trình nghiệp vụ}, Đại học Bách Khoa Đại học Quốc gia thành phố Hồ Chí Minh.
    \bibitem{postgresql} PostgreSQL, \textit{PostgreSQL 14.1 Documentation}, [Online, URL\: \url{https://www.postgresql.org/}].
    \bibitem{python} Python, \textit{Python 3.10.2 Documentation}, [Online, URL\: \url{https://www.python.org/}].
    \bibitem{qualtrics} Qualtrics, \textit{What is a Net Promoter Score?}, [Online, URL\: \url{https://www.qualtrics.com/au/experience-management/customer/measure-nps/}].
    \bibitem{raileanu22} Grigore Raileanu, \textit{NPS, CSAT and CES \- Customer Satisfaction Metrics to Track in 2024}, [Online, URL\: \url{https://www.retently.com/blog/customer-satisfaction-metrics/}, truy cập ngày 9\-2\-2022].
    \bibitem{raileanu23} Grigore Raileanu, \textit{CSAT\: Definition, Calculation \& 2023 Benchmarks}, [Online, URL\: \url{https://www.retently.com/blog/customer-satisfaction-score-csat/}, truy cập ngày 1\-6\-2023].
    \bibitem{rallis20} Rallis, I., Markoulidakis, I., Georgoulas, I., \& Kopsiaftis, G. (2020), \textit{A novel classification method for customer experience survey analysis}.
    \bibitem{rasmus} Rasmus, GD, Svensson, \textit{Contextualizing Customer Feedback: A Research-through-Design Approach}, Uppsala University, Department of Informatics and Media.
    \bibitem{regmi17} Regmi, P. R., Waithaka, E., Paudyal, A., Simkhada, P., \& Van Teijlingen, E. (2017), \textit{Guide to the design and application of online questionnaire surveys}, Nepal Journal of Epidemiology.
    \bibitem{rotella11} Rotella, P., \& Chulani, S. (2011), \textit{Implementing quality metrics and goals at the corporate level}.
\end{thebibliography}